Measuring security performance in the Android ecosystem

### 2015-06-08 ccs.tex
The importance of quantification

\todo{We need to rerun the analysis on the AOSP data for its current state}
\todo{What is the significance of having done this quantification?}
\section{Threat model and attack vectors}
\label{sec:threatmodel}

>>>>

We have quantified the complexity due to the large number of participants in the ecosystem, the many updates flowing between them and the high latency of updates reaching devices.

\section{Threat model and attack vectors}
\label{sec:threatmodel}
